% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\signature{Russell Shomberg}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}
  %{Ms. Terri Roberts \\
   % Senior Staff Recruiter \\
   % XYZ Corporation \\
   % Rt. 56 \\
   % Anytown, New Jersey 05867} 

\begin{center}
\large\bf RUSSELL J. SHOMBERG \\
20 Rhode Island Ave \\ Newport, RI 02840 \\ (203) 376-9329
\end{center} 
\vfill % forces letterhead to top of page


 
\opening{Dear Employer:} 
 
\noindent I am Russell Shomberg. I studied Mechanical Engineering at Boston University before starting a career as an Cryptologic Warfare Officer in the US Navy. After five years, I requested seperation in order to return to engineering. Specifically, I intend to be part of the growing drive towards sustainable public infrastructure. I learned of your company's offer through LKJJKKLJKLJK and believe I would be a good match.

\noindent Through the Navy, I have gained experience working both autonomously and in teams. In my role, as an officer, I took imprecise directions and leveraged my resources to quickly produce detailed results. The military expects officers to be constantly completing the next qualification and learning their boss's job. I excelled at this process inside the Navy and have always been seeking new skill sets in my personal life. Please let me know if you feel I lack an specific skills required for your job offer. Likely, I can arrange to learn just about anything.

\noindent Please see my attached resume. Additionally, I attached my final Fitness Report written by CAPT Gagnon, the Commanding Officer of my primary command, and a PIM written by CDR Answee, the Commanding Officer who I supported on my final deployment. Unfortunately, classification prevents revealing details from my previous work. I hope these documents provide some clarity into the challenges involved. Otherwise, I am happy to answer questions.

\noindent I respectfully request you invite me for an interview to discuss my qualifications and our mutual goals. I promise to impress. Currently, I am out of the country and best reached by email, though I can arrange a phone call or video conference if necessary. For more information about me, please take a look at my linkedin profile, my website, or just google my name! I'm happy to answer any questions you may have.


 

 
\closing{Very respectfully,}
 
 
\encl{}  				% Enclosures

\end{letter}
 

\end{document}




