\runsubsection{Viking Equipment}
\descript{| Project Manager}
\location{April 2017 - Present | Deep River, CT}
\begin{tightemize}
\item Managed planning, design, and installation of repair facilities for five auto shop installations consisting of a total of over \$3 million of installed equipment and systems.
\item Built detailed CAD layouts of shop systems and equipment.
\item Designed and built 15 custom systems for pnuematic tools, fluid delivery, and exhaust removal.
\item Managed to equipment and human resources to ensure concurrent equipment installations were scheduled into building construction phases.
\item Interfaced with customer, general contractor, archetect, and service managers to develop facility requirements and ensure building design allowed for optimal equipment selection.
\end{tightemize}
\sectionsep

\runsubsection{Multiple US Submarines}
\descript{| Intelligence Officer }
\location{August 2014 - December 2016 | Pacific Fleet}
\begin{tightemize}
\item Four operational deployments and 12 training missions on six ships.
\item Managed 15 sailors and six equipment racks from preparations to post mission reporting.
\item Responsible for determining mission objectives and risk mitigation based on limited information.
\item One of four Department Heads, responsible for all operational planning.
\item Produced detailed post-mission reports and data packages.
\item Selected by Cyber Fleet to evaluate submarines and Information Warfare Teams for deployment readiness. 
\end{tightemize}
\sectionsep

\runsubsection{Subsurface Ops Department}
\descript{| Division Officer}
\location{August 2014 – December 2016 | NIOC Hawaii}
\begin{tightemize}
\item Responsible for management of multiple divisions of over 40 sailors.
\item Oversaw daily training and administrative functions.
\item Scheduled deployment cycles based on available manning.
\end{tightemize}
\sectionsep

\runsubsection{Subsurface Ops Department}
\descript{| Department Action Officer}
\location{August 2014 – December 2016 | NIOC Hawaii}
\begin{tightemize}
\item Primary substitute for Department Head during leave of other absences responsible for over 400 sailors.
\item Selected to perform internal inspection. Designed and implemented correctional policies.
\item Routinely selected to represent department or command for meetings and briefs with to Admirals, Staff Officers, and other VIPs.
\item Provided training and evaluated qualifications of enlisted and more junior officers throughout command.
\end{tightemize}
\sectionsep

\runsubsection{Fleet Information Ops Center}
\descript{| Battle Watch Captain }
\location{December 2013 – August 2014 | NIOC Hawaii}
\begin{tightemize}
\item Led team of 9 sailors responsible for providing threat warning and time relevant intelligence reporting to forward deployed ships and aircraft.
\item Proactively distributed information through intelligence and operational networks through formal briefs and reports, informal teleconferences, phone calls, emails, and in-person conversations.
\item Provided NIOC Hawaii's Commanding Officer a daily Operations Brief.
\item Represented commanding officer in daily conference with the Commander of Cyber Fleet.
\end{tightemize}
\sectionsep

\runsubsection{Temporary Duty Stations}
\descript{| Cryptologic Warfare Officer}
\location{May 2012 – December 2013 | Monterey, CA \& Panama City, FL \& Pensacola, FL}
\sectionsep

