\documentclass[line, margin]{resume}

\begin{document}
\name{Russell J. Shomberg}
\address{20 Rhode Island Dr \\ Newport, RI 02840 \\ (203) 376-9329}
\address{http://russellshomberg.com \\ LinkedIn \\ russellshomberg@gmail.com}

\begin{resume}

  \section{EXPERIENCE}
  
  \begin{format}
    \title{l}\employer{r}\\
    \dates{r}\\
    \body\\
    \location{l}\\
  \end{format}
  
  \employer{Navy Information Operations Command}
  \title{Cryptologic Warfare Officer}
  \dates{DEC 2013 - DEC 2016}
  \location{Pearl Harbor, HI}
  
  \begin{position}
    \begin{itemize}
    \item Direct Support Officer Sub-Surface
      \begin{itemize}
       \item 4 operational deployments and 12 training missions on six seperate ships.
       \item Led 15 sailors and six equipment racks.
       \item 1 of 5 Department Heads, responsible for all operational planning.
       \item Sole Intelligence Officer in a radio-silent environment, responsible for evaluating risk vs reward in mission goals.
       \item Produced detailed reports and data packages viewed by high ranking officials including Chief of Naval Operations and the President.
       \item Selected by Command Cyber Fleet to evaluate submarines and cryptologic teamsfor deployment readiness. 
      \end{itemize}
    \item Battle Watch Captain
      \begin{itemize}
- Led team of 9 sailors responsible for providing threat warning and time relevant intelligence reporting to forward deployed ships and aircraft.
- Proactively distrubuted information through intelligence and operational networks through formal briefs and reports, informal teleconferences, phone calls, emails, and in-person conversations.
- Provided NIOC Hawaii's Commanding Officer a daily hour long Operations Brief.
- Represented command in daily conference with the Commander of Cyber Fleet.
      \end{itemize}
    \item Division Officer
      \begin{itemize}
- Responsible for management of one of more divisions of approximently 40 sailors.
- Oversaw daily training and administrative functions.
- Scheduled deployment cycles based on available manning.
      \end{itemize}
    \item Department Action Officer
      \begin{itemize}

      \end{itemize}
    \end{itemize}
  \end{position}
  
  \employer{Various Joint and Naval Commands}
  \title{Junior Naval Officer}
  \dates{MAY 2012 - DEC 2013}
  \location{MA, CA, PR, FL}

  \begin{position}
    This probably just gets a sentence
  \end{position}

  % alternate format
  %\textit{Cryptologic Warfare Officer} \hfill Navy Information Operations Command Hawaii DEC 2013-DEC 2016 \\
  %Description here\\ [10pt]
  
  \section{TECHNICAL SKILLS}
  \begin{itemize}
  \item Need
  \item Some
  \item Skills
  \item Here
  \end{itemize}
  
  \section{NON-TECHNICAL SKILLS}
  \begin{itemize}
  \item Need
  \item Some
  \item Skills
  \item Here
  \end{itemize}
  
  \section{PROFESIONAL CERTIFICATIONS}
  \begin{tabular}{l l}
    January 2017 & \textbf{\textit{Commissioned Leutenant, US Navy Reserves}} \\ [5pt]
  \end{tabular}
  
  \section{EDUCATION} 
  Bachelor of Science in Mechanical Engineering \\
  Boston University, May 2012 \\
  \\
  Associate of Art in Spanish \\
  Defense Language Institute, April 2013 \\
  
  
\end{resume}
\end{document}
